### 2020-06-30 introduction.tex

% introduce LPL asynchronous duty cycle media access
Smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing". 
Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes, avoiding the severe data leakage effectively~\cite{eiband2017understanding}. For example, a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password shown on screen without any equipment. 
% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

@@

Unfortunately, none of existing work can mitigate the new threat model. Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm. \cl{supplement elements for long range, blurred input and the recognized results.}}
	\label{illustration_of_system}
\end{figure}

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
Assuming the victim is scanning messages in life, the attacker can raise his commercial smartphone with powerful lenses and our SR network to the victim stealthily, even from a long range (e.g., 1.5 meters far away within the visual angle of 30$^{\circ}$). As the camera zooms in, he can take 20 to 30 snapshots continuously in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames. This process can take about 2 seconds with the consistent content and position for the screen of the victim. Benefited from our multi-frame SR neural network, those blurred snapshots can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim in real time. Note that multi-type contents can be recovered accurately on the smartphone screen of the victim, covering numbers, English and Chinese characters. The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim’s screen.

@@

\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally" captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction" than ``interpolation". Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character. 

>>>>

% introduce LPL asynchronous duty cycle media access
Smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing''. 
Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes, avoiding the severe data leakage effectively~\cite{eiband2017understanding}. For example, a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password shown on screen without any equipment.

% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

@@

Unfortunately, none of existing work can mitigate the new threat model. Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm. \cl{supplement elements for long range, blurred input and the recognized results.}}
	\label{illustration_of_system}
\end{figure}

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
Assuming the victim is scanning messages in life, the attacker can raise his commercial smartphone with powerful lenses and our SR network to the victim stealthily, even from a long range (e.g., 1.5 meters far away within the visual angle of 30$^{\circ}$). As the camera zooms in, he can take 20 to 30 snapshots continuously in burst mode, with about 0.05 ~ 0.1 seconds of interval between frames. This process can take about 2 seconds with the consistent content and position for the screen of the victim. Benefited from our multi-frame SR neural network, those blurred snapshots can be then aligned, cropped, and processed, delivering a holistic threat model for acquisition of high-resolution contents of the victim in real time. Note that multi-type contents can be recovered accurately on the smartphone screen of the victim, covering numbers, English and Chinese characters. The above procedure can be automated by an app and repeated every few seconds, giving the attacker a continuous surveillance over the victim's screen.

@@

\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction'' than ``interpolation''. Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.
